\begin{itemize}[leftmargin=0.65cm]
\vspace{-0.1cm}
\item[23.]{Masterson, M., De, K., Panagiotou, C., Kara, E., {\bf Lu, W.}, et al., {JWST's First View of Tidal Disruption Events: Compact, Accretion-driven Emission Lines and Strong Silicate Emission in an Infrared-selected Sample}, {\it ApJL}, 988, 2, (2025)(aug) \href{https://ui.adsabs.harvard.edu/abs/2025ApJ...988L..48M}{\underline{PDF}}}

\vspace{-0.1cm}
\item[22.]{Feng, Y., Zhang, Y., Xie, J., Yang, Y., Qu, Y., et al. {\bf (Lu, W.)}, {Multi-year polarimetric monitoring of four CHIME-discovered repeating fast radio bursts with FAST}, {\it Science China Physics, Mechanics, and Astronomy}, 68, 8, (2025)(aug) \href{https://ui.adsabs.harvard.edu/abs/2025SCPMA..6889511F}{\underline{PDF}}}

\vspace{-0.1cm}
\item[21.]{Yao, Y., Chornock, R., Ward, C., Hammerstein, E., Sfaradi, I., et al. {\bf (Lu, W.)}, {A Massive Black Hole 0.8 kpc from the Host Nucleus Revealed by the Offset Tidal Disruption Event AT2024tvd}, {\it ApJL}, 985, 2, (2025)(jun) \href{https://ui.adsabs.harvard.edu/abs/2025ApJ...985L..48Y}{\underline{PDF}}}

\vspace{-0.1cm}
\item[20.]{Somalwar, J., Ravi, V., Yao, Y., Guolo, M., Graham, M., et al. {\bf (Lu, W.)}, {The First Systematically Identified Repeating Partial Tidal Disruption Event}, {\it ApJ}, 985, 2, (2025)(jun) \href{https://ui.adsabs.harvard.edu/abs/2025ApJ...985..175S}{\underline{PDF}}}

\vspace{-0.1cm}
\item[19.]{Wharton, R., Majid, W., Sherman, M., Connor, L., Kocz, J., et al. {\bf (Lu, W.)}, {High-frequency Fast Radio Burst Search of Nearby Star-forming Galaxies M77 and M82}, {\it ApJ}, 984, 2, (2025)(may) \href{https://ui.adsabs.harvard.edu/abs/2025ApJ...984..119W}{\underline{PDF}}}

\vspace{-0.1cm}
\item[18.]{Earl, N., French, K., Ramirez-Ruiz, E., Auchettl, K., Raimundo, S., et al. {\bf (Lu, W.)}, {AT 2020nov: Evidence for Disk Reprocessing in a Rare Tidal Disruption Event}, {\it ApJ}, 983, 1, (2025)(apr) \href{https://ui.adsabs.harvard.edu/abs/2025ApJ...983...28E}{\underline{PDF}}}

\vspace{-0.1cm}
\item[17.]{Goodwin, A., Mummery, A., Laskar, T., Alexander, K., Anderson, G., et al. {\bf (Lu, W.)}, {A Second Radio Flare from the Tidal Disruption Event AT2020vwl: A Delayed Outflow Ejection?}, {\it ApJ}, 981, 2, (2025)(mar) \href{https://ui.adsabs.harvard.edu/abs/2025ApJ...981..122G}{\underline{PDF}}}

\vspace{-0.1cm}
\item[16.]{Zhuang, J., Shen, R., Mou, G., {\bf Lu, W.}, {Interaction of an Outflow with Surrounding Gaseous Clouds as the Origin of Late-time Radio Flares in Tidal Disruption Events}, {\it ApJ}, 979, 2, (2025)(feb) \href{https://ui.adsabs.harvard.edu/abs/2025ApJ...979..109Z}{\underline{PDF}}}

\vspace{-0.1cm}
\item[15.]{Yao, P., Quataert, E., Jiang, Y., {\bf Lu, W.}, White, C., et al., {Star‑Disk Collisions: Implications for Quasi-periodic Eruptions and Other Transients near Supermassive Black Holes}, {\it ApJ}, 978, 1, (2025)(jan) \href{https://ui.adsabs.harvard.edu/abs/2025ApJ...978...91Y}{\underline{PDF}}}

\vspace{-0.1cm}
\item[14.]{Yao, Y., Guolo, M., Tombesi, F., Li, R., Gezari, S., et al. {\bf (Lu, W.)}, {Subrelativistic Outflow and Hours-timescale Large-amplitude X-Ray Dips during Super-Eddington Accretion onto a Low-mass Massive Black Hole in the Tidal Disruption Event AT2022lri}, {\it ApJ}, 976, 1, (2024)(nov) \href{https://ui.adsabs.harvard.edu/abs/2024ApJ...976...34Y}{\underline{PDF}}}

\vspace{-0.1cm}
\item[13.]{Kirsten, F., Ould-Boukattine, O., Herrmann, W., Gawro{\'n}ski, M., Hessels, J., et al. {\bf (Lu, W.)}, {A link between repeating and non-repeating fast radio bursts through their energy distributions}, {\it Nature Astronomy}, 8, (2024)(mar) \href{https://ui.adsabs.harvard.edu/abs/2024NatAs...8..337K}{\underline{PDF}}}

\vspace{-0.1cm}
\item[12.]{Sheikh, S., Farah, W., Pollak, A., Siemion, A., Chamma, M., et al. {\bf (Lu, W.)}, {Characterization of the repeating FRB 20220912A with the Allen Telescope Array}, {\it MNRAS}, 527, 4, (2024)(feb) \href{https://ui.adsabs.harvard.edu/abs/2024MNRAS.52710425S}{\underline{PDF}}}

\vspace{-0.1cm}
\item[11.]{Ryder, S., Bannister, K., Bhandari, S., Deller, A., Ekers, R., et al. {\bf (Lu, W.)}, {A luminous fast radio burst that probes the Universe at redshift 1}, {\it Science}, 382, 6668, (2023)(oct) \href{https://ui.adsabs.harvard.edu/abs/2023Sci...382..294R}{\underline{PDF}}}

\vspace{-0.1cm}
\item[10.]{Yao, Y., Ravi, V., Gezari, S., van Velzen, S., {\bf Lu, W.}, et al., {Tidal Disruption Event Demographics with the Zwicky Transient Facility: Volumetric Rates, Luminosity Function, and Implications for the Local Black Hole Mass Function}, {\it ApJL}, 955, 1, (2023)(sep) \href{https://ui.adsabs.harvard.edu/abs/2023ApJ...955L...6Y}{\underline{PDF}}}

\vspace{-0.1cm}
\item[9.]{Wang, B., Xu, H., Jiang, J., Xu, J., Niu, J., et al. {\bf (Lu, W.)}, {Atlas of dynamic spectra of fast radio burst FRB 20201124A}, {\it Chinese Physics B}, 32, 2, (2023)(feb) \href{https://ui.adsabs.harvard.edu/abs/2023ChPhB..32b9801W}{\underline{PDF}}}

\vspace{-0.1cm}
\item[8.]{Andreoni, I., Coughlin, M., Perley, D., Yao, Y., {\bf Lu, W.}, et al., {A very luminous jet from the disruption of a star by a massive black hole}, {\it Nature}, 612, 7940, (2022)(dec) \href{https://ui.adsabs.harvard.edu/abs/2022Natur.612..430A}{\underline{PDF}}}

\vspace{-0.1cm}
\item[7.]{Xu, H., Niu, J., Chen, P., Lee, K., Zhu, W., et al. {\bf (Lu, W.)}, {A fast radio burst source at a complex magnetized site in a barred galaxy}, {\it Nature}, 609, 7928, (2022)(sep) \href{https://ui.adsabs.harvard.edu/abs/2022Natur.609..685X}{\underline{PDF}}}

\vspace{-0.1cm}
\item[6.]{Somalwar, J., Ravi, V., Dong, D., Graham, M., Hallinan, G., et al. {\bf (Lu, W.)}, {The Nascent Milliquasar VT J154843.06+220812.6: Tidal Disruption Event or Extreme Accretion State Change?}, {\it ApJ}, 929, 2, (2022)(apr) \href{https://ui.adsabs.harvard.edu/abs/2022ApJ...929..184S}{\underline{PDF}}}

\vspace{-0.1cm}
\item[5.]{Feng, Y., Li, D., Yang, Y., Zhang, Y., Zhu, W., et al. {\bf (Lu, W.)}, {Frequency-dependent polarization of repeating fast radio bursts{\textemdash}implications for their origin}, {\it Science}, 375, 6586, (2022)(mar) \href{https://ui.adsabs.harvard.edu/abs/2022Sci...375.1266F}{\underline{PDF}}}

\vspace{-0.1cm}
\item[4.]{Makhathini, S., Mooley, K., Brightman, M., Hotokezaka, K., Nayana, A., et al. {\bf (Lu, W.)}, {The Panchromatic Afterglow of GW170817: The Full Uniform Data Set, Modeling, Comparison with Previous Results, and Implications}, {\it ApJ}, 922, 2, (2021)(dec) \href{https://ui.adsabs.harvard.edu/abs/2021ApJ...922..154M}{\underline{PDF}}}

\vspace{-0.1cm}
\item[3.]{Bij, A., Lin, H., Li, D., van Kerkwijk, M., Pen, U., et al. {\bf (Lu, W.)}, {Kinematics of Crab Giant Pulses}, {\it ApJ}, 920, 1, (2021)(oct) \href{https://ui.adsabs.harvard.edu/abs/2021ApJ...920...38B}{\underline{PDF}}}

\vspace{-0.1cm}
\item[2.]{Connor, L., Shila, K., Kulkarni, S., Flygare, J., Hallinan, G., et al. {\bf (Lu, W.)}, {Galactic Radio Explorer: An All-sky Monitor for Bright Radio Bursts}, {\it pasp}, 133, 1025, (2021)(jul) \href{https://ui.adsabs.harvard.edu/abs/2021PASP..133g5001C}{\underline{PDF}}}

\vspace{-0.1cm}
\item[1.]{Kool, E., Reynolds, T., Mattila, S., Kankare, E., P{\'e}rez-Torres, M., et al. {\bf (Lu, W.)}, {AT 2017gbl: a dust obscured TDE candidate in a luminous infrared galaxy}, {\it MNRAS}, 498, 2, (2020)(oct) \href{https://ui.adsabs.harvard.edu/abs/2020MNRAS.498.2167K}{\underline{PDF}}}
\end{itemize}